Flexibility reduces social donations

### 2021-11-17 article-elsevier/article-elsevier.Rmd
corrige outputs para compilar

```{r graficos_donaciones_1, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", out.width="40%"}
#grafico con donaciones y cambio de leyes
ggplot(Donaciones_total, aes(x = Fecha , y = monto_total_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Total donation")+
  ylim(0,20000)+
  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
  annotate("text", x = as.Date("2008-09-11"), y = 19500, label = "Law 19885")+
  annotate("text", x = as.Date("2010-01-01"), y = 18000, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 20000, label = "Law 20565")+
  annotate("text", x = as.Date("2012-04-08"), y = 16000, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 19000, label = "Law 20900_2")+
  ggtitle("Donations: Total amount over time")

@@

```{r graficos_donaciones_2, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", out.width="40%"}

@@

```{r graficos_donaciones_3, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="20%"}
ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Donation to Mixed Fund")+
  ylim(0,2500)+
  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
  annotate("text", x = as.Date("2008-09-11"), y = 2500, label = "Law 19885")+
  annotate("text", x = as.Date("2009-11-01"), y = 2000, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 2200, label = "Law 20565")+
  annotate("text", x = as.Date("2012-04-08"), y = 1850, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 2000, label = "Law 20900_2")+
  ggtitle("Donations: Mixed Found amount over time")

>>>>

```{r graficos_donaciones_1, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", dev='png',dpi=200, out.width="70%"}
#grafico con donaciones y cambio de leyes
ggplot(Donaciones_total, aes(x = Fecha , y = monto_total_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Total donation")+
  ylim(0,20000)+
  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
  annotate("text", x = as.Date("2008-09-11"), y = 19500, label = "Law 19885")+
  annotate("text", x = as.Date("2010-01-01"), y = 18000, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 20000, label = "Law 20565")+
  annotate("text", x = as.Date("2012-04-08"), y = 16000, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 19000, label = "Law 20900_2")+
  ggtitle("Donations: Total amount over time")

@@

```{r graficos_donaciones_2, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, dev='png', dpi=200, out.width="70%"}

@@

```{r graficos_donaciones_3, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, dev='png', dpi=200, out.width="70%"}
ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +
  # Make points small and semi-transparent since there are lots of them
  geom_point(size = 0.5, alpha = 0.5) + 
  # Add vertical line
  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
  # Add labels
  labs(x = "Date", y = "Donation to Mixed Fund")+
  ylim(0,2500)+
  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
  annotate("text", x = as.Date("2008-09-11"), y = 2500, label = "Law 19885")+
  annotate("text", x = as.Date("2009-11-01"), y = 2000, label = "Law 20316")+
  annotate("text", x = as.Date("2011-01-01"), y = 2200, label = "Law 20565")+
  annotate("text", x = as.Date("2012-04-08"), y = 1850, label = "Law 20900_1")+
  annotate("text", x = as.Date("2016-04-14"), y = 2000, label = "Law 20900_2")+
  ggtitle("Donations: Mixed Found amount over time")
